---
title: "hw05-molly-li"
author: "Molly Li"
date: "4/25/2018"
output: github_document
---



The purpose of this assignment is to create an R package that implements functions for simulating rolling a die. And then use the package to approximate probabilities to the famous Chevalier De Mere’s dice problems.

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
The goal is to program two classes of objects: a regular "die" with six sides, and an object "roll" (i.e. the rolls of a "die").

1) Object "die"
```{r}
check_sides <- function(sides = c(1,2,3,4,5,6)){
  if(length(sides) != 6){stop("\n'object' must be of sides of 6")}
  return('TRUE')
}

check_prob <- function(prob = rep(1/6,6)){
  if(length(prob) != 6 | !is.numeric(prob) ){stop("\n 'probability' must be a numeric vector of length 6") }
  if(any(prob) < 0 | any(prob > 1)){stop("\n value of 'probability' must be inbetween 0 and 1")}
  if(sum(prob) != 1){stop("\n 'probability' must add up to 1")}
  return("TRUE")
}
 
die <- function(sides = c(1,2,3,4,5,6), prob = rep(1/6,6)){
  check_sides(sides)
  check_prob(prob)
  res <- list(side = sides, prob = prob)
  class(res) <- "die"
  return(res)
}

print.die<- function(x){
  cat('object "die" \n\n')
  cd <- data.frame(
    side = x$side, prob = x$prob)
  print(cd)
}

die()
```

```{r}
weird_die <- die(sides = c('i', 'ii', 'iii', 'iv', 'v', 'vi')) 
loaded_die <- die(prob = c(0.075, 0.1, 0.125, 0.15, 0.20, 0.35))
bad_die <- die(sides = c('a', 'b', 'c', 'd', 'e'))
```

```{r}
bad_die1 <- die(sides = c('a', 'b', 'c', 'd', 'e', 'f'), prob = c(0.2, 0.1, 0.1, 0.1, 0.5, 0.1))
```

2) Object "roll"
```{r}
check_times <- function(x){
  if(x %% 1 != 0 |x < 0 ){stop(" 'times' must be a positive integer")}
  FALSE
}

roll <- function(die, times =1){
  check_times(times)
  rolls <- sample(die$side, size = times, replace = TRUE, prob = die$prob)
  abc <- list(rolls = rolls, sides = die$side, prob = die$prob, total = times )
  class(abc) <- "roll"
  return(abc)
}

print.roll <- function(x){
  cat("object 'roll' \n\n")
  print(x$rolls)
}
```

```{r}
fair_die <- die() 
set.seed(123)
fair50 <- roll(fair_die, times = 50) 
fair50
```

```{r}
names(fair50)
fair50$rolls
fair50$sides
fair50$prob
fair50$total
```

```{r}
 # string die
str_die <- die(
sides = c('a', 'b', 'c', 'd', 'e', 'f'),
prob = c(0.075, 0.1, 0.125, 0.15, 0.20, 0.35))
# roll 20 times
set.seed(123)
str_rolls <- roll(str_die, times = 20) 
names(str_rolls)
str_rolls
```


3) Summary method for "roll" objects
```{r}
summary.roll <- function(x){
  freqs <- data.frame(
  side = x$sides,
  count = as.vector(table(x$rolls)),
  prop = as.vector(table(x$rolls))/x$total
  )
  obj <- list(freqs = freqs) 
  class(obj) <- "summary.roll"
  return(obj)
}

print.summary.roll <- function(x){
  cat("summary 'roll' \n\n")
  print(x$freqs)
}
```

```{r}
set.seed(123)
fair_50rolls <- roll(fair_die, times = 50) 
fair50_sum <- summary(fair_50rolls)
fair50_sum
```

```{r}
 # what's in the summary
class(fair50_sum)
```

```{r}
names(fair50_sum)
fair50_sum$freqs
```

4) Plot methd for "roll" objects
Write a plot method for "roll" objects—i.e. plot.roll(). You need to graph a barchart of frequencies (relative frequencies of 1’s, 2’s, 3’s, 4’s, 5’s, and 6’s). Use barplot() to implement this method.
```{r}
plot.roll <- function(x){
  height <- as.vector(table(x$rolls))/x$total
  name <- x$sides
  title <- paste0("Frequencies in a series of", x$total, 'die rolls')
  return(barplot(height = height, names.arg = name,xlab = 'sides of die', ylab = "relative frequencies",main = title))
}

```

```{r}
 # plot method
plot(fair_50rolls)
```

5) Additional Methods
Also, write functions for the following methods:
• an extraction method "[" to extract the value of a given roll.
• a replacement method "[<-" to replace the value of a given roll.
• an addition "+" method to add more rolls.
```{r}
"[.roll" <- function(x, i){
  if(!is.numeric(i)|i == 0|i> length(x$rolls)){stop("i is invalid")}
  x$rolls[i]
}
```

```{r}
"[<-.roll" <- function(x, i, value){
    if(!is.numeric(i)|i == 0|i> length(x$rolls)){stop("i is invalid")}
    if(value %in% x$sides == FALSE){stop("value is invalid")}
    newvector <- x$rolls
    newvector[i] <- value
    return(newvector)
}
```

```{r}
set.seed(123)
fair_die <- die()
fair500 <- roll(fair_die, times = 500)
fair500[500] <- 4
fair500
```


#De Mere's problem
###Problem I
```{r}
Game1 <- function(x) {
  win = 0
  for (i in 1:x) {
  if (6 %in% roll(die(), 4)$rolls) {
    win = win + 1
  }}
  return(win/x)
}
Game1(1000)
1-(5/6)^4
```

###Problem II
```{r}
Game2 <- function(x) {
  win = 0
  kk = 0
  for (i in 1:x) {
    for (j in 1:24) {
   rollpair <- roll(die(), 2)  
    kk[j] = sum(rollpair$rolls == 6)
    }
    if (2 %in% kk) {
      win = win + 1
    }
  }
  return(win/x)
}
Game2(1000)
1-(35/36)^24
```

